Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
added baseline paragraph to sec. 7

>>>>

\paragraph{Preliminary results on actor-critic.}As mentioned, another variance-reduction technique in policy gradient is to employ baselines, or \textit{critics}. This tool is orthogonal to the methods described in this paper, and the theoretical results of Section \ref{sec:conv} are general in this sense. In the experiments described so far, we compared against the so-called \textit{actor-only} G(PO)MDP, \ie without baseline. In order to move towards a more general understanding of the problem of variance in policy gradient, we also test SVRPG in an \textit{actor-critic} scenario. To do so, we use the more challenging mujoco Half-cheetah task, a 3D locomotion task that has a larger state-action space than Swimmer. Table \ref{tab:1} also reports the comparison between SVRPG and G(PO)MDP on Half-cheetah using the critic suggested in \cite{duan2016benchmarking} for both algorithms. Results are promising, showing that a combination of baseline usage and SVRG-like variance reduction can yield an improvement that the two techniques alone are not able to achieve.
